---
title: "Lab 07 - Modelling course evaluations"
author: "INSERT NAME HERE"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
evals %>% 
  ggplot(mapping=aes(x=score)) +
  geom_histogram(binwidth=0.2)
```

- Distribution is heavily skewed left
- Students tend to rate courses quite highly.
This is not what I would expect from a school.




2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
evals %>% 
  ggplot(mapping=aes(x=score, y=bty_avg)) +
  geom_point()

evals %>% 
  ggplot(mapping=aes(x=score, y=bty_avg)) +
  geom_jitter()
```

The `geom_point` version misrepresented the number of points at each score, because some scores have the same average, so were rendered on top of each other. Jitter adds some random variation to make the trend more apparent.

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(bty_avg ~ score, data = evals)
```

y = scorex+intercept,
bty = 0.52... score + 2.222

```{r tidy-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

bty_hat = 2.22 + 0.526 X score 

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit}
# add your plot here. Hint, you can add the regression line using geom_smooth()
evals %>% 
  ggplot(mapping=aes(x=score, y=bty_avg)) +
  geom_jitter() + 
  geom_smooth(method = "lm", se=FALSE)
```

3. Interpret the slope of the linear model in context of the data.


d/dscore bty_hat = 0.526
for each additional point the score goes up, the beauty increases by 0.56 points on average

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

the beauty rating for teachers with a score of 0 is expected, on average to be 2.22 (this makes sense, since a score can be 0)

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(score_bty_fit)$adj.r.squared * 100
```

This model is not very good, or the data is not very linear with respect to the beauty (in this case I think it's that the data isn't very linear)

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic}
score_bty_aug <- augment(score_bty_fit$fit)
  ggplot(score_bty_aug, mapping=aes(.resid, .fitted)) +
  geom_point()
```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
# ... 
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

*Add your narrative here. Use in-line code!*

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

```{r eval = FALSE}
ggplot(___) + ...
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
